---
output: html_document
date: "2024-12-05"
params:
  org_code: 'RMC'
  plot_attend: TRUE
  plot_brea: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown report for site `r params$org_code`

In simple terms the varible within the markdown doc is params$xxx

Make sure that you have declared them in the YAML to begin

This time have added a couple more varables to the top

We will put the markdown within a cat statement which in turn will be within an **if** statement.  This is a base R if statement.

In this case attendances is set as `r params$plot_attend`

```{r, echo = TRUE,  warning=FALSE}

if (params$plot_attend == TRUE) {
  cat('### Plot attendances')
  cat('\n')
  cat('\n')
  plot_site(dat, params$org_code, 'attendances')
}



```

In this case breaches is set as `r params$plot_brea`

```{r, echo = TRUE,  warning=FALSE}

if (params$plot_brea == TRUE) {
  cat('### Plot breaches')
  cat('\n')
  cat('\n')
  plot_site(dat, params$org_code, 'breaches')
}



```

If we set echo to false, in the places where FALSE was selected, we would not see anything at all.   That metric simply would not be there.


